|

### 2021-07-23 03-Chp-Systematic-Review.Rmd
End of day:

Table \@ref(tab:incl-studies-character) shows the characteristics

@@

Include here:

-   PRISMA Flowchart

-   Summary of types of study

-   Summary of locations (use evidence map)

-   Summary of diagnostic criteria used

-   Summary of risk of bias

-   Long table, horizontally.

A common theme across the studies was a lack of data on vascular dementia. This is particularly interesting as lipids and statins are primarily a vascular disease. There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading). For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of

@@

@@

### Hazard ratios vs risk/odds ratios

@@

### Meta-n

@@

### Dose response meta-analysis

>>>>

Table \@ref(tab:studyCharacteristics-table) shows the characteristics

@@

<!--- TODO Figures and tables to include here:

-   PRISMA Flowchart (done)

-   Summary of types of study (half done)

-   Summary of locations (half done)

-   Summary of diagnostic criteria used (done)

-   Summary of risk of bias (not done)

--->

```{r cohortLocationsSetup, include = FALSE}

```

(ref:cohortLocations-cap) Geographical distribution of study cohorts

(ref:cohortLocations-scap) Geographical distribution of study cohorts

```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
```
<!----------------------------------------------------------------------------->

Many of the included studies were conducted in European countries (Figure \@ref(fig:cohortLocations).

A common theme across the studies was a lack of data on vascular dementia. This is particularly interesting as lipids and statins are primarily a vascular disease. There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading). For vascular dementia, few studies examined this outcome, primarily because of the absence (until recently) of

@@

<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->

@@

@@

### Meta-analysis of statin use and hypercholesteroleamia

Straight-forward random effects meta-analysis of

```{r primaryFigures, include = FALSE}

```

<!----------------------------------------------------------------------------->
(ref:fpStatins-cap) __Forest plot showing effect of statins:__

(ref:fpStatins-scap) Forest plot showing effect of statins

```{r fpStatins, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpStatins-cap)', out.width='100%', fig.scap='(ref:fpStatins-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
```
<!----------------------------------------------------------------------------->

@@

### Dose response meta-analysis of lipid levels

### 2021-07-23 04-Chp-CPRD-Analysis.Rmd
End of day:

An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]

@@

In this analysis, missing data were handled using a multiple imputation approach. Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression. As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.

@@

Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset. As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019a] to investigate the impact of multiple imputation on the results.

@@

Immortal time bias covers two distinct but related types of bias. The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010a] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.

@@

In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis. It should be noted that due to the large amount of missing data (e.g. `r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data. In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009b]

@@

However, the findings of this analysis are subject to several limitations. There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure. As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents. Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019b]

>>>>

An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]

@@

In this analysis, missing data were handled using a multiple imputation approach. Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression. As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.

@@

Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset. As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.

@@

Immortal time bias covers two distinct but related types of bias. The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.

@@

In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis. It should be noted that due to the large amount of missing data (e.g. `r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data. In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]

@@

However, the findings of this analysis are subject to several limitations. There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure. As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents. Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
